Type Refinements for the Working Class

### 2015-11-12 paper.tex
fix up

   We will write $\HPGenJ{\Upsilon}{\Gamma}{\Omega}{\mathcal{J}}$ for
   $\GenJ{\Omega'}{\mathcal{J}}$, where
   $\Lookup{\Omega'}{\MV{m}}{\MkValence{\Upsilon,\vec{\sigma}}{\Gamma,\vec{\tau}}{\tau}}$
   if $\Lookup{\Omega}{\MV{m}}{\MkValence{\vec{\sigma}}{\vec{\tau}}{\tau}}$.
   Additionally, for clarity we will often write
   $\GenJ{\MV{m}:\sigma}{\mathcal{J}}$ rather than
   $\GenJ{\MV{m}:\MkValence{\cdot}{\cdot}{\sigma}}{\mathcal{J}}$; likewise, in
   the body of $\mathcal{J}$, when there is a contextually salient
   $\vec{u}$, we will simply write $\MV{m}$ rather than the more proper
   $\MApp{\MV{m}}{\vec{u}}{\cdot}$.

>>>>

   We will write $\HPGenJ{\Upsilon}{\Gamma}{\Omega}{\mathcal{J}}$ for
   $\GenJ{\Omega'}{\mathcal{J}}$, where
   $\Lookup{\Omega'}{\MV{m}}{\MkValence{\Upsilon,\vec{\sigma}}{\Gamma,\vec{\tau}}{\tau}}$
   if $\Lookup{\Omega}{\MV{m}}{\MkValence{\vec{\sigma}}{\vec{\tau}}{\tau}}$.
   Additionally, for clarity we will often write
   $\GenJ{\MV{m}:\sigma}{\mathcal{J}}$ rather than
   $\GenJ{\MV{m}:\MkValence{\cdot}{\cdot}{\sigma}}{\mathcal{J}}$; likewise, in
   the body of $\mathcal{J}$, when there are contextually salient
   $\vec{u}$, $\vec{x}$, we will simply write $\MV{m}$ rather than the more proper
   $\MApp{\MV{m}}{\vec{u}}{\vec{x}}$.
